% -*-latex-*-
% 
% For questions, comments, concerns or complaints:
% thesis@mit.edu
% 
%
% $Log: cover.tex,v $
% Revision 1.8  2008/05/13 15:02:15  jdreed
% Degree month is June, not May.  Added note about prevdegrees.
% Arthur Smith's title updated
%
% Revision 1.7  2001/02/08 18:53:16  boojum
% changed some \newpages to \cleardoublepages
%
% Revision 1.6  1999/10/21 14:49:31  boojum
% changed comment referring to documentstyle
%
% Revision 1.5  1999/10/21 14:39:04  boojum
% *** empty log message ***
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.3  93/05/17  17:06:29  starflt
% Added acknowledgements section (suggested by tompalka)
% 
% Revision 1.2  92/04/22  13:13:13  epeisach
% Fixes for 1991 course 6 requirements
% Phrase "and to grant others the right to do so" has been added to 
% permission clause
% Second copy of abstract is not counted as separate pages so numbering works
% out
% 
% Revision 1.1  92/04/22  13:08:20  epeisach

% NOTE:
% These templates make an effort to conform to the MIT Thesis specifications,
% however the specifications can change.  We recommend that you verify the
% layout of your title page with your thesis advisor and/or the MIT 
% Libraries before printing your final copy.
\clearpage
\subsection*{\begin{center}
Acknowledgments
\end{center}}

%\noindent
\begin{singlespace}
I would like to express my deepest gratitude to my supervisor Prof. Aitchison, for his guidance, support and most importantly his trust. We did not meet on a regular basis and he just had to trust that I was doing what I said I was doing. The lack of regular and constant supervision was a boon that I was very grateful for, as it gave me the space to experiment and play around with different ideas by myself, before ultimately running them through him. 

I also want to thank Dr. Farshid Bahrami for taking the time to explain his idea to me, dumbed down quite significantly so that I could understand it. I'd also like to thank him for giving me his FORTRAN code - it was a great starting point and meant that a lot of the programming (which would have taken atleast an extra month to code) was already done, and that I could just go straight to the brute force search of the parameter space (after constraining it appropriately). 

I also want to thank Arnab Dewanjee and Xiao Sun for the invaluable time and effort they expended in teaching me the basics of the various machines in the many clean rooms around the U of T campus. Were it not for them the SEM images in this thesis would never have existed, not to mention the quality of the fabricated structures would have been absolutely horrid.

I would also like to take this opportunity to thank Dr. Alexander Tsukernik and Dr. Edward Huaping Xu for their technical skills that they so generously offered.

I'm also indebted to my friend Adam Shaw who took the time to read over my thesis and point out the many many errors that I had made (a fair few of which were rather embarrassing).

Finally, I'd like to thank my parents for their constant love, support, and (when appropriate) criticism. 
\end{singlespace}



\clearpage